Hector Permafrost

### 2019-09-13 analysis/paper/paper.Rmd
Add note about permafrost surface C fraction
Add markdown captions

library(hector.permafrost.emit) # Or use devtools::load_all('.', quiet = T) if your code is in script files, rather than as functions in the `/R` diretory
```

@@

@@

@@

@@

@@

@@

>>>>

library(hector.permafrost.emit) # Or use devtools::load_all('.', quiet = T) if your code is in script files, rather than as functions in the `/R` diretory

n <- 0
mdcap <- function(text) {
  n <<- n + 1
  out <- sprintf("**Figure %d**: %s", n, text)
  if (grepl("gfm", knitr::opts_knit$get("rmarkdown.pandoc.to"), ignore.case = TRUE)) {
    out
  } else {
    invisible(NULL)
  }
}

fig <- function(...) {
  filepath <- here("analysis", "figures", ...)
  knitr::include_graphics(file_in(filepath))
}
```

@@

Actual permafrost surface C fraction is around 30% [@schuur_2015_climate].

@@

`r mdcap(global_ts_cap)`

@@

`r mdcap(global_scatter_cap)`

@@

`r mdcap(biome_ts_cap)`

@@

`r mdcap(biome_scatter_cap)`

@@

`r mdcap(biome_sensitivity_cap)`
